R Notebook

### 2019-07-18 analysis/EvolTalk.Rmd
about to do some major reorganization

```{r}
library(assertthat)
library(ggplot2)
library(dplyr)
library(tidyr)
library(PopGenome)
library(stringr)
library(data.table)
library(magrittr)
library(wrapr)
library(foreach)
library(IDPmisc)

@@

MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#Ploidy
MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(Dom, traj_ploidy, Depth, Breadth, Height) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

#disentangling
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

#drift
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_color_manual(guide=F, values = c("black", "red")) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(10000) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/100000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, Height, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + scale_color_manual(guide=F, values = c("black", "red")) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16), axis.ticks.y = element_blank())

@@

ee = ms %>% filter(fuseGen==1 & driftGen %in% c(1,0,10000) & dom == 0.5 & sampGen %in% c(1,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width),) %>% select(-data) %>% unnest()

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.h, "Breadth" = width.h / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fay & Wu's H" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Fay & Wu's H`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "1" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0) %>% mutate("Magnitude" = height.e, "Breadth" = width.e / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Zeng's E" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~`Zeng's E`, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.fst < 60000) %>% mutate("Magnitude" = height.fst, "Breadth" = width.fst / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("Fst" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~Fst, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(sampGen == "10000" & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, traj_ploidy, same_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = as.factor(same_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Trajectory Ploidy", labels = c("2", "4", "8")) + scale_color_manual(guide=F, values = c("black","red")) + facet_wrap(~TajD, scales = "free_y", labeller = label_both) + ylab("") + xlab("Coalescent Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

ee %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & fuseGen=="1" & recomb == "5e-08" & dom=="0.5" & N=="10000" & driftGen == 0 & width.taj < 100000) %>% mutate("Magnitude" = height.taj, "Breadth" = width.taj / 10000, same_ploidy = ifelse(sim_ploidy == traj_ploidy, 1, 0)) %>% select(sim_ploidy, sampGen, Magnitude, Breadth) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("TajD" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Generations since\nFixation") + ylab("") + xlab("Coalescent Ploidy") + facet_wrap(~TajD, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

>>>>

```{r}
library(assertthat)
library(ggplot2)
library(dplyr)
library(tidyr)
library(PopGenome)
library(stringr)
library(data.table)
library(magrittr)
library(wrapr)
library(foreach)
library(IDPmisc)
library(wesanderson)

@@

MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(name = "Dominance") + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#Ploidy
MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.1, 0.5, 0.9)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi, Size = breadth.pi * depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth, Size) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(Dom), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Dominance", values=wes_palette("Royal1")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("Ploidy") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#Just additive
MS2.f %>% filter(sim_ploidy == traj_ploidy & mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Dom = factor(case_when(dom == 0.1 ~ "Partial Recessivity", dom == 0.5 ~ "Additivity", dom == 0.9 ~ "Partial Dominance"), levels = c("Partial Recessivity", "Additivity", "Partial Dominance")), Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(Dom, traj_ploidy, Magnitude, Breadth) %>% melt(., id.var = c("Dom", "traj_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(traj_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_discrete(guide = F) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#disentangling
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0,1) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, Magnitude, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + scale_color_manual(guide=F, values = c("black", "red")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("\n\n") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

#drift
MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(0) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Magnitude = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + geom_boxplot(outlier.shape = NA) + scale_color_manual(guide=F, values = c("black", "red")) + scale_fill_manual(name = "Trajectory Ploidy", values = wes_palette("Moonrise2")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

MS2.f %>% filter(mu==1e-08 & N == 10000 & s =="0.01" & driftGen %in% c(10000) & sampGen == 1 & dom %in% c(0.5)) %>% mutate(Height = (log(min.pi, 10)), Breadth = breadth.pi/10000, Depth = depth.pi) %>% select(sim_ploidy, traj_ploidy, driftGen, Depth, Breadth, same_ploidy) %>% melt(., id.var = c("sim_ploidy", "traj_ploidy", "driftGen", "same_ploidy")) %>% ggplot(., aes(y = value, fill = as.factor(traj_ploidy), x = as.factor(sim_ploidy), color = same_ploidy)) + scale_color_manual(guide=F, values = c("black", "red")) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Trajectory Ploidy",values = wes_palette("Moonrise2")) + facet_wrap(~variable, scales = "free_y") + ylab("") + xlab("") + theme_bw() + theme(axis.text.y=element_text(size = 16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

@@

getStat = function(dat, stat){return(median(unlist(dat[stat]), na.rm = T))}

ee = ms %>% filter(fuseGen==1 & driftGen %in% c(1,0,10000) & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

#All metrics together for sampGen
#Magnitude

dd = ms %>% filter(sim_ploidy == traj_ploidy & fuseGen==1 & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

dd = ms %>% filter(sim_ploidy == traj_ploidy & s == "0.01" & recomb == "5e-08" & N=="10000" & driftGen == 0 & sampGen %in% c(1,1000,10000)) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep, driftGen)) %>% mutate(height.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$height), width.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")$width), height.fst = map(data, ~getDims(.)$height), med.fst = map(data, ~getStat(., "fst")), width.fst = map(data, ~getDims(.)$width), height.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$height), width.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")$width), height.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$height), width.e = map(data, ~getDims(., y.metric = "Zeng.E_1")$width), height.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$height), width.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")$width), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

#Winner
dd %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != 40.5) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylim(0,7) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~Magnitude) + theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

dd.points = dd %>% filter(dom %in% c("0.1", "0.9") & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj * width.taj / 2, "FayWuH" = height.h * width.h / 2, "ZengsE" = height.e * width.e / 2) %>% select(sim_ploidy, dom, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen", "dom")) %>% mutate("Area" = variable) %>% filter(value != 40.5) %>% group_by(sim_ploidy, sampGen, dom, variable) %>% summarize(median = median(value))

gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = (height.fst - med.fst) * width.fst, "Dxy" = (height.dxy - med.dxy) * width.dxy, "XPEHH" = height.xp * width.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + ylab("Peak Size") + xlab("Ploidy") + facet_wrap(~Magnitude, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

# dd %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = height.taj, "FayWuH" = height.h, "ZengsE" = height.e) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Magnitude, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
# 
# dd %>% filter(traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("TajD" = width.taj, "FayWuH" = width.h, "ZengsE" = width.e) %>% select(sim_ploidy, sampGen, TajD, FayWuH, ZengsE) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Breadth" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Breadth, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))

# gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = height.fst - med.fst, "Dxy" = height.dxy - med.dxy, "XPEHH" = height.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Magnitude" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Magnitude, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
# 
# gg %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & recomb == "1e-08" & N=="10000" & driftGen == 0)  %>% mutate("Fst" = width.fst, "Dxy" = width.dxy, "XPEHH" = width.xp) %>% select(sim_ploidy, sampGen, Fst, Dxy, XPEHH) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate("Breadth" = variable) %>% filter(value != -9) %>% ggplot(., aes(y = value / 10000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + scale_fill_manual(name = "Generations since\nFixation", values = wes_palette("Royal2")) + ylab("") + xlab("Ploidy") + facet_wrap(~Breadth, labeller = label_both, scales = "free_y") +theme_bw() + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18), axis.text.x=element_text(size=16), axis.title.x=element_text(size=18), legend.text = element_text(size=16), legend.title = element_text(size=18), strip.text = element_text(size=16))
